GSE158433: GMEA of DNA methylation and RNA-seq differences in lung squamous cell carcinoma

### 2022-05-24 GSE158433/GSE158433_gmea.Rmd
add integrative analysis
priority

mres <- mitch_calc(x=meth, genesets=genesets)

@@

int_res <- mitch_calc(int,genesets=genesets)

@@

mres <- mitch_calc(x=pmeth, genesets=genesets)

@@

int_res <- mitch_calc(int,genesets=genesets)
int_res_tbl <- int_res$enrichment_result

>>>>

mres <- mitch_calc(x=meth, genesets=genesets,priority="effect")

@@

plot(int,xlim=c(-100,100))
abline(h=0,lty=2,lwd=2,col="red")
abline(v=0,lty=2,lwd=2,col="red")

uu <- length(which(int$meth>0 & int$rna>0))
ud <- length(which(int$meth>0 & int$rna<0))
dd <- length(which(int$meth<0 & int$rna<0))
du <- length(which(int$meth<0 & int$rna>0))

int_res <- mitch_calc(int,genesets=genesets,priority="effect")

@@

mres <- mitch_calc(x=pmeth, genesets=genesets,priority="effect")

@@

plot(int)
abline(h=0,lty=2,lwd=2,col="red")
abline(v=0,lty=2,lwd=2,col="red")

uu <- length(which(int$meth>0 & int$rna>0))
ud <- length(which(int$meth>0 & int$rna<0))
dd <- length(which(int$meth<0 & int$rna<0))
du <- length(which(int$meth<0 & int$rna>0))

int_res <- mitch_calc(int,genesets=genesets,priority="effect")
